\section{Actors and Use Cases}
\label{sec:use-cases}

Three core use cases---publishing an appliance, using an appliance,
and authorizing an appliance---expose the required features and the
actors for appliance management in both federated and non-federated
environments.  The primary actors and their roles are:
\begin{description}
\item[Creator] Makes a new appliance and desires to publish the image
  for her own or someone else's use.
\item[Endorser] Validates an appliance against certain criteria and
  issues an endorsement to this effect.
\item[User] A scientist or engineer who wants to find and to use
  existing appliances.
\item[Admin] The cloud administrator responsible for
  maintaining the cloud services and the security of the platform.
\end{description}

\subsection{Publishing an Appliance}

Despite automation, appliance creation is a tedious, error-prone, and
lengthy process.  Creators with the expertise to create new
appliances often want to share their appliances with a larger
community for wider use and better testing.  Doing so requires
publishing the appliance.

To publish the appliance, the creators must make the appliance's
contents and metadata available.  At a minimum, the metadata needs to
include information about the appliance's operating system, service
configuration, and access parameters.  The appliance's contents and
metadata may be provided either as separate files or as a single file.

\subsection{Using an Appliance}

Users want to avoid the effort required to create an appliance by
reusing an existing one, if possible.  A central registry allows users
to discover appropriate appliances based, for example, on the
operating system, what services are enabled, etc.  Complete appliance
metadata is crucial for finding appropriate appliances.

Users also want to verify the origin of the metadata and the integrity
of the appliance's contents.  An endorsement of the appliance is
critical for establishing trust in the appliance itself.  The creator
is usually also an endorser of an appliance, but appliances can and
often are endorsed by multiple people.  This allows, for instance,
third party certification of appliances.

Once users find a suitable appliance, they want to run an instance of
that appliance on a cloud infrastructure.  This requires transport of
the appliance's contents to the cloud infrastructure.  Although users
can do this manually, cloud infrastructures should handle the
transport transparently given the appliance identifier.

\subsection{Authorizing an Appliance}

Most users of cloud infrastructures have little or no experience with
system management.  They are unfamiliar with best practices and
techniques for securing machines, for example limiting SSH access and
configuration of firewalls.  Consequently, cloud administrators have a
strong interest in ensuring that users run appliances that have been
built with these best practices in mind.

Before allowing a user to start an appliance, cloud administrators
will want to authorize that particular appliance.  Based on appliance
metadata, administrators can define a policy that suits their needs,
ranging from very restrictive policies, which allow only appliances
endorsed by one particular person, to open policies, which permit all
appliances except those with known security problems.
