\section{Bioinformatics Usecase}
\label{sec:bioinfo}

Biologists and bioinformaticians simultaneously use many of the bioinformatics tools from the thousands available in the international community. Frequently they also need to combine multiple software packages to study their data with either public, or their own, analysis pipelines. Helping scientists to easily identify appliances that could assist in the analysis of their data is essential, especially in the context of federated clouds. In such environments appliances can be created by different experts and could be available in several places.

As identifying and running the relevant bioinformatics appliances could be difficult, IDB have developed a custom tools description coupled with the StratusLab Marketplace where the bioinformatics tools are referenced and tagged with RDF metadata. These metadata can be used to select the right bioinformatics appliance according to the desired tools (\textit{e.g.} BLAST, ClustalW2) or the kind of analysis to perform (\textit{e.g.} sequence or structural analysis). We have deployed a marketplace devoted to biology in Lyon (IDB cloud~\cite{idbcloud}) where we are creating bioinformatics appliances for external labs and projects. We are helping bioinformatics experts to define virtual appliances with pre-installed tools and workflows, and helps scientists to deploy them, on demand, on national research infrastructures.

Bioinformatics experts pre-install the bioinformatics tools related to the analysis they are targeting with the new appliance. They describe these 'biotools' in the appliance manifest according to a schema described in Figure~\ref{fig:biotool-schema}, and register this bioinformatics-enhanced manifest in the Marketplace. Then bioinformaticians and biologists can query the Marketplace for a requested tool, for example ClustalW2 to do multiple sequence alignment of genes or proteins, to identify which appliances are providing this tool. Finally running the desired bioinformatics appliances is easy as for any cloud appliance.

\begin{figure}
 \begin{center}
    \small
    \begin{lstlisting}
        <ex:biotool rdf:parseType="Resource">
            <dcterms:identifier>clustalw2
            </dcterms:identifier>
            <dcterms:description>ClustalW 2
               : multiple sequence alignment
            </dcterms:description>
            <slterms:version>2.1</slterms:version>
        </ex:biotool>
    \end{lstlisting}
     \caption{Example `biotool' metadata}
    \label{fig:biotool-schema}
  \end{center}
\end{figure}
