%%
%% An example for producing a StratusLab deliverable, milestone, or report.
%% 

\documentclass{../stylesheet/stratuslab}

\usepackage{rotating}

\newcommand{\replaceable}[1]{\ensuremath{\langle}#1\ensuremath{\rangle}}
\newcommand{\cmd}[1]{\texttt{#1}}

%%
%% Define metadata for the document
%%

% Provide fixed date and year for final version.  Use the date format below.
\date{\dmyformat\today}
%\date{31 January 2010}
\newcommand{\copyrightyear}{\yearonly\today}
%\newcommand{\copyrightyear}{2010}

% Define document type: "Deliverable", "Milestone", or "Report"
\doctype{Technical Note}

% Define the document ID.  Ex. "D3.2" for second deliverable of WP3.
\docid{TN-Marketplace}

% Define the document version.  Ex. "1.2".
\docversion{3.0}

% Define the title.  Capitalize each non-trivial word.
\title{StratusLab Marketplace}

% Define the abstract.  It should be a good summary of the reports material and conclusions.
\abstract{%
StratusLab provides a complete, open-source solution for deploying an ``Infrastructure as a Service'' cloud infrastructure.  Use of the cloud requires the use of prepared machine and disk images.  The StratusLab Marketplace serves as a registry for shared images.  It is at the center of the image handling mechanisms in the StratusLab distribution.
}

\begin{document}

\maketitle

% CONTRIBUTORS LIST
% \contributor{Last Name, First name}{Organization}{contributed to ... (use references, i.e., \ref{}

\begin{contributors}
  \contributor{Mohammed AIRAJ}{CNRS-LAL}{All}
  \contributor{Marc-Elian BEGIN}{SixSq}{All}
  \contributor{Stuart KENNY}{TCD}{All}
  \contributor{Charles LOOMIS}{CNRS-LAL}{All}
  \contributor{David O'CALLAGHAN}{TCD}{All}
\end{contributors}

%
% REVISION HISTORY
%
\begin{history}
  \historyitem{0.1}{13 May 2010}{Initial version for comment.}
  \historyitem{1.0}{26 Jan. 2011}{Collect information in JIRA and previous notes.}
  \historyitem{1.0}{2 Feb. 2011}{Update URL mapping.}
  \historyitem{1.1}{2 Feb. 2011}{Update version number.}
  \historyitem{2.0}{12 Feb. 2011}{Update URL mapping, schemas, and examples.}
  \historyitem{3.0}{2 Mar. 2011}{Add use cases and workflows involving the Marketplace\@.}
\end{history}

%
% FRONT MATTER (remove lists of figures/tables if there are none)
%
\tableofcontents
\listoftables

\include{introduction}

\include{implementation}

\include{metadata}

\include{security-considerations}

\include{related-components}

\bibliography{marketplace}

\end{document}
